Draft

### 2022-07-22 ms.tex
intro, caption, discussion revised by k;

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases 
across the cosmic time \citep{1982MNRAS.200..115S,1992MNRAS.259..725S}. 
Comparing the local massive BH mass density and the integration of quasar luminosity function up to $z\sim$ 5, 
\citet{2002MNRAS.335..965Y} demonstrate the constraints on the BH accretion history and their radiative effeciency.
Extrapolation of such argument toward higher redshifts ($z\gtrsim$ 6) is unwarranted, 
due to the limitation of current capabilities of observing the high-$z$ quasar population \citep{2019BAAS...51c.121F}. 
Nevertheless, 
% while its essence is appropriate to BH evolution of all redshifts. 
in the era of the James Webb Space Telescope (JWST) and forthcoming facilities 
e.g., the Roman Space Telescope (RST) and Euclid, 
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year, 
and the establishment of BH-galaxy coevolution \citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}.

Tracing back from $z\sim$ 6, BH seed formation is the starting point to shape the early evolution of the BH population.
From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$), 
the properties of high-$z$ BH seeds are extensively modeled by simulations and semi-analytical works 
\citep[e.g.,][Toyouchi 2022]{2001ApJ...546..635O,2002Sci...295...93A,2006ApJ...652....6Y,2011MNRAS.416.2748I,
2012ApJ...756...93H,2013ApJ...778..178H,2014MNRAS.439.3798F,
2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}. 
Environmental factors which modulate the Pop III star formation have been assessed, 
including (i) external ratiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$ 
\citep{2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S},
(ii) baryonic streaming motion which drives the gas against gravitational collapse 
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H}
and 
(iii) violent mergers of the parent dark matter halo which dynamically excite the gas 
\citep{2003ApJ...592..645Y,2019Natur.566...85W}. 
These factors prevail in some environments at high redshifts and facilitate massive Pop III and even supermassive star formation, 
which contribute to the heavy seed scenario of supermassive BH formation at $z\gtrsim$ 6 
\citep[see a review by][]{2020ARA&A..58...27I}.

@@

%%%%%%%
%    Fig. 1
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{seedBHMF_z.pdf}
\caption{
Seed BH mass distribution formed in different redshift ranges . 
Each panel includes a redshift span of 10, 
with the newly formed BHs denoted by the hatched regions, 
and the cumulative BHs formed previously by the blue region.
The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
Overall, the seed BH mass ranges from $\sim 10^2$ to $\gtrsim 10^5~\Msun$, 
imprinted with the various parent halo growth histories and environmental $\vbsm$. 
}
\label{fig:seedmf}
\end{figure*}

@@

%%%%%%%
%    Fig. 3
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=180mm]{contour.pdf}
\caption{
Posterior distributions of all the model parameters with $\fseed=0.1$ and 0.01, 
including the marginalized one dimensional projection and the two dimensional distribution between every two parameters. 
All the parameters converge to a single peak, 
and specially the $\log\delta$ is confined above the artificial $-3$ barrier, 
which is sufficiently low and can be neglected in the model.
}
\label{fig:contour}
\vspace{5mm}
\end{figure*}
%

@@

@@

For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
%, which is sufficiently small and should be marginalized out. 
This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
$\sim 30$ times on average, toward the cosmic time of $t_{\rm H}\gtrsim 900$ Myr at $z\simeq 6$.
The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
observed in the rest-frame UV spectra (e.g., Eilers+2018, Davies+ 2019).\red{KI: we need to figure out 
if their $t_Q$ is the quasar age or lifetime, or something else?}
More detailed comparison is discussed in \S\ref{sec:evol}.

@@

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{fits_MF.png}
\caption{
Fit of BHMF at $z=$ 6 by the best-fit parameters (orange line), with one sigma spread (shaded region) for $\fseed=$ 0.1 and 0.01. 
The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
% error of observation
}
\label{fig:fitmf}
\end{figure*}

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{fits_LF.png}
\caption{
Fit of QLF at $z=$ 6, by the best-fit parameters and one sigma spread as described in \ref{fig:fitmf}. 
The blue data points with error bars label the QLF from the observation by \citet{2018ApJ...869..150M}.
}
\label{fig:fitlf}
\end{figure*}

@@

\vspace{2mm}
\subsection{Cosmological evolution of BHMF and QLF}\label{sec:cosm}
% \red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
% Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
% Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{BHMF_rhoz.png}
\caption{
Left panel: BHMF at $z$ from 6 to 10. The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions are the one sigma spread. 
Right panel: the mass density of BHs with $\Mbh > 10^7~\Msun$, integrated from the BHMF in the left panel.
}
\label{fig:BHMF_rhoz}
\end{figure*}

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{QLF_rhoz.png}
\caption{
Left panel: QLF at $z$ from 6 to 10. The solid lines denote modeled QLF produced by the best-fit parameters 
and the shaded regions are the one sigma spread. 
Right panel: the cumulative number density of quasars with $\Muv <-26$, integrated from the QLF in the left panel.
}
\label{fig:QLF_rhoz}
\end{figure*}

@@

Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
us to probe the statistical BH evolution at higher redshifts.
As a fiducial case, we take the best-fit parameters of BH growth for $\fseed=$ 0.01,
where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
We apply the result to construction of BHMFs and QLFs at higher redshifts and give implications for
the future explorations of high-$z$ quasars.
In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the BHMFs at five different redshifts of $z=6-10$.
For all the redshifts, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations.
From higher to lower redshifts, the number density of BHs heavier than $M_\bullet = 10^7~\Msun$ increases
and the high-mass tail of the distribution is extended owing to efficient growth of the most massive BH population.
%The number density of BHs with $\Mbh=10^7~\Msun$ emerging from high redshifts increase by a factor of $\sim 4$ per unit redshift.
In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we also present the cumulative mass density of BHs with $\Mbh \geq M_{\rm min}$ in a comoving volume,
defined by the integration of the BHMF as
%
\begin{equation}
 \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh,
\end{equation}
%
%as a function of redshift.
where we set the minimum mass to $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$.
This result shows that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
%
\begin{equation}
\rho_\bullet(z)
%= \rho_{\bullet 0}\cdot e^{k_{\rm M}(z-6)}
\simeq \rho_{\bullet,0}~ 10^{k_{\rm M}(z-6)},
\end{equation}
%
where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.
On the other hand, the stellar mass density of the quasar progenitor halos is calculated as
%
\begin{equation}
\rho_{\star}(z)
\simeq f_\star n_{\Mh} M_h~ 10^{k_{\rm h}(z-6)},
\end{equation}
%
where $f_\star(\equiv M_\star/\Mh)$ is the mass ratio of the galaxy stellar mass to the DM halo mass and
$n_{\Mh}$ is the number density of quasar host halos with $\Mh$ in a comoving volume at $z=6$; namely,
the value of $n_{\Mh}\Mh \simeq (6.2-99)\times 10^6~\Msun~{\rm Mpc}^{-3}$.
We here express the mass growth of the DM halo with a functional form of $\propto 10^{k_{\rm h} z}$,
which nicely reproduces the mass growth of DM halos
\citep[e.g.,][]{2002ApJ...568...52W,2008MNRAS.383..615N,2008MNRAS.388.1792N,2010MNRAS.406.2267F}
\footnote[3]{
In fact, this redshift dependence leads to a halo-mass growth rate of $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$,
which has been understood based on the extended Press-Schechter formalism and also derived by
a fit to merger trees from cosmological N-body simulations \citep{2013MNRAS.435..999D}.}.
% The redshift dependence yields the cosmic BH growth rate in the matter-dominated universe
% as $\dot{\rho}_\bullet \propto \rho_\bullet (1+z)^{5/2}$ or

@@

% where $\bar{k}_{\rm M} \equiv k_{\rm M} \ln 10 \simeq -1.84$.
% \red{KI: I'm not sure what we discuss here... One thing is the cosmic SFR density (Madau's plot).
% Is there something like Madau's plot but for DM halos?}
% The exponential dependence on redshift is reminiscent of the cosmic galaxy mass growth
% $M_{\star} \propto e^{-B z}$, as a consequnce of the assumption of fixed galaxy to DM halo mass ratio,
% and the growth rate of DM halos in the extended Press-Schechter formalism
% $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$ \citep{2008MNRAS.383..615N}.
% Our results suggest that the cumulative massive BH mass density growing in galactic nuclei also follows
% an exponential evolution with redshift,
% which is statistically in agreement with the host halo and galaxy growth.
The star-to-halo mass ratio is assumed to be $f_\star =0.01$ for those quasar progenitor halos at $z>6$
% (UNIVERSEMACHINE; Behroozi et al. 2019).
\citep[fits by code {\tt UNIVERSEMACHINE} in][]{2019MNRAS.488.3143B}.
%https://ui.adsabs.harvard.edu/abs/2019MNRAS.488.3143B/abstract
With those values, we estimate the cumulative stellar-to-BH mass ratio for high-$z$ quasars as
%
\begin{equation}
\frac{\rho_{\star}(z)}{\rho_{\bullet}(z)}
\simeq 2.5\times 10^{3} \left(\frac{f_\star}{0.01}\right)
~ 10^{(k_{\rm h}-k_{\rm M})(z-6)},
\end{equation}
% wli now
\red{KI: please check the value of $k_{\rm h}-k_{\rm M}$.}
\blue{
where $k_{\rm h} \approx -0.16 $ for the parent halo growth histories.
}
Therefore, at $z\sim 6$ the bulge-to-BH mass ratio $\sim O(10^3)$ for the entire BH population (i.e., low-mass BHs and low-luminosity quasars) 
is broadly consistent with those seen in the local universe, although SMBHs observed as high-$z$ quasars
appear to be overmassive compared to the local relation \citep{2013ApJ...773...44W,2020A&A...637A..84P} \dots.

Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
%The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
\red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
Also, you could compare your results with Aaron Yung's results.}
In the right panel of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
The rapid decline toward higher redshifts is nicely characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.

@@

>>>>

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S,1992MNRAS.259..725S}.
Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
the integration of the quasar luminosity function based on multi-wavelength observations,
the cosmic BH accretion history and their radiative efficiency are nicely constrained \citet{2002MNRAS.335..965Y}
\red{KI: add more references, Ueda+14, Delvecchio+14, Marconi?, and some Shankar's papers}.

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2019BAAS...51c.121F} \red{KI: you could find better reference in this Decadal Survey?}.
Nevertheless,... \red{KI: you could say the current status of $z=6$ QLFs/BHMFs; citing Jiang+16, 18, Willott+10, HSC papers.}
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.

Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
semi-analytical studies
%From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$),
%the properties of high-$z$ BH seeds are extensively modeled by simulations and semi-analytical works
%\citep[e.g.,][Toyouchi 2022]{2001ApJ...546..635O,2002Sci...295...93A,2006ApJ...652....6Y,2011MNRAS.416.2748I,
%2012ApJ...756...93H,2013ApJ...778..178H,2014MNRAS.439.3798F,
%2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}.
\red{KI: I think here we should cite more general citations: Begelman+2006; Tanaka \& Haiman 2009; Hirano+14, 15,
Toyouchi+2022, one Natarajan+Volonteri's paper discussing the mass function, Valiante+2018, Sassano+21}
Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
%factors which modulate the Pop III star formation have been assessed,
(i) H$_2$ photo-dissociating irradiation from nearby galaxies
%irradiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$
\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V}
\red{KI: add Chon+16},
(ii) supersonic baryonic streaming motion that delays gas collapse in halos
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H} \red{KI: add Inayoshi, Li \& Haiman 18, Schauer +17},
and
(iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
\citep{2003ApJ...592..645Y, 2019Natur.566...85W} \red{KI: add Latif's Nature paper, Mayer+10 or 15}.
Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
without vigorous fragmentation \citep{2014MNRAS.445L.109I} \red{KI: add Becerra+15, Latif+16}, and allow supermassive stars
with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers \red{cite Hosokawa+13, Woods+19?, Schleicher+13, Toyouchi+22}.
Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
\red{cite Dijkstra+08, Ahn+09, Inayoshi \& Tanaka 15}, recent studies by Lupi+21 and Li+21 found that the heavy-seed formation
can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
and the frequency of halo mergers.
%These factors prevail in some environments at high redshifts and facilitate massive Pop III and even supermassive star formation,
%which contribute to the heavy seed scenario of supermassive BH formation at $z\gtrsim$ 6
%\citep[see a review by][]{2020ARA&A..58...27I}.

\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
Also, I remember one paper of our former postdoc, Kim.
Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
Please add more (I might miss some relevant papers.)}
\blue{
High-z
}

@@

%%%%%%%
%    Fig. 1
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{seedBHMF_z.pdf}
\caption{
Mass distribution of seed BHs formed in quasar host galaxies at different redshifts ($50\lesssim z \lesssim 10$).
%Each panel includes a redshift span of 10, 
In each panel, the cumulative number distribution of BHs are shown and 
the contribution from newly-born BHs at the redshift interval are denoted with the hatched region.
%with the newly formed BHs denoted by the hatched regions, 
%and the cumulative BHs formed previously by the blue region.
The majority of seed BHs form in the epoch of $40\lesssim z \lesssim 20$.
%The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
Overall, the seed BH mass distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
imprinted with various pathways of parent halo assembly and environmental effects as discussed in \S\ref{sec:seed}.
}
\label{fig:seedmf}
\end{figure*}

@@

%%%%%%%
%    Fig. 3
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=180mm]{contour.pdf}
\caption{
Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ and 0.01, 
along with the marginalized one dimensional projection.
% and the two dimensional distribution between every two parameters. 
The distribution of three parameters ($\tau$, $\lambda_0$, and $\alpha$) show single peaks,
meaning the convergence of those parameters.
The distribution of $\log\delta$ is relatively broader but suggests that the value of $\delta$
is sufficiently low and thus the mass-dependent growth model is excluded.
% confined above the artificial $-3$ barrier, 
%which is sufficiently low and can be neglected in the model.
}
\label{fig:contour}
\vspace{5mm}
\end{figure*}
%

@@

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{fits_MF.png}
\caption{
The BH mass function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
For comparison, the BHMF inferred by \citetalias{2010AJ....140..546W} is overlaid (blue curve and shaded region).
The data is used for the model parameter fitting.
%.The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
% error of observation
}
\label{fig:fitmf}
\end{figure*}

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{fits_LF.png}
\caption{
The quasar luminosity function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
%as described in \ref{fig:fitmf}. 
The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
}
\label{fig:fitlf}
\end{figure*}

@@

For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
%, which is sufficiently small and should be marginalized out. 
This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
$\sim 30$ times on average, over the cosmic time of $t_{\rm H}\simeq 800$ Myr at $z\simeq 6$.
The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
observed in the rest-frame UV spectra (e.g., Eilers+2018, Davies+ 2019).\red{KI: we need to figure out 
if their $t_Q$ is the quasar age or lifetime, or something else?}
More detailed comparison is discussed in \S\ref{sec:evol}.

@@

@@

\vspace{2mm}
\section{Cosmological evolution of BH mass and quasar luminosity function}\label{sec:cosm}
%\red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
%Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
%Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{BHMF_rhoz.png}
\caption{
{\it Left panel}: BH mass functions at different redshifts of $6\leq z \leq 10$.
The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
evaluated by the integration of the BHMF shown in the left panel.
The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.8$.
}
\label{fig:BHMF_rhoz}
\end{figure*}

@@

Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
us to probe the statistical BH evolution at higher redshifts.
As a fiducial case, we take the best-fit parameters of BH growth for $\fseed=$ 0.01,
where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
We apply the result to construction of BHMFs and QLFs at higher redshifts and give implications for
the future explorations of high-$z$ quasars.

\subsection{Black hole mass function}

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the BHMFs at five different redshifts of $z=6-10$.
For all the redshifts, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations.
From higher to lower redshifts, the number density of BHs heavier than $M_\bullet = 10^7~\Msun$ increases
and the high-mass tail of the distribution is extended owing to efficient growth of the most massive BH population.
%The number density of BHs with $\Mbh=10^7~\Msun$ emerging from high redshifts increase by a factor of $\sim 4$ per unit redshift.
In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we also present the cumulative mass density of BHs with $\Mbh \geq M_{\rm min}$ in a comoving volume,
defined by the integration of the BHMF as
%
\begin{equation}
 \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh,
\end{equation}
%
%as a function of redshift.
where we set the minimum mass to $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$.
This result shows that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
%
\begin{equation}
\rho_\bullet(z)
%= \rho_{\bullet 0}\cdot e^{k_{\rm M}(z-6)}
\simeq \rho_{\bullet,0}~ 10^{k_{\rm M}(z-6)},
\end{equation}
%
where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.
On the other hand, the stellar mass density of the quasar progenitor halos is calculated as
%
\begin{equation}
\rho_{\star}(z)
\simeq f_\star n_{\Mh} M_h~ 10^{k_{\rm h}(z-6)},
\end{equation}
%
where $f_\star(\equiv M_\star/\Mh)$ is the mass ratio of the galaxy stellar mass to the DM halo mass and
$n_{\Mh}$ is the number density of quasar host halos with $\Mh$ in a comoving volume at $z=6$; namely,
the value of $n_{\Mh}\Mh \simeq (6.2-99)\times 10^6~\Msun~{\rm Mpc}^{-3}$.
We here express the mass growth of the DM halo with a functional form of $\propto 10^{k_{\rm h} z}$,
which nicely reproduces the mass growth of DM halos
\citep[e.g.,][]{2002ApJ...568...52W,2008MNRAS.383..615N,2008MNRAS.388.1792N,2010MNRAS.406.2267F}
\footnote[3]{
In fact, this redshift dependence leads to a halo-mass growth rate of $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$,
which has been understood based on the extended Press-Schechter formalism and also derived by
a fit to merger trees from cosmological N-body simulations \citep{2013MNRAS.435..999D}.}.
% The redshift dependence yields the cosmic BH growth rate in the matter-dominated universe
% as $\dot{\rho}_\bullet \propto \rho_\bullet (1+z)^{5/2}$ or

@@

% where $\bar{k}_{\rm M} \equiv k_{\rm M} \ln 10 \simeq -1.84$.
% \red{KI: I'm not sure what we discuss here... One thing is the cosmic SFR density (Madau's plot).
% Is there something like Madau's plot but for DM halos?}
% The exponential dependence on redshift is reminiscent of the cosmic galaxy mass growth
% $M_{\star} \propto e^{-B z}$, as a consequnce of the assumption of fixed galaxy to DM halo mass ratio,
% and the growth rate of DM halos in the extended Press-Schechter formalism
% $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$ \citep{2008MNRAS.383..615N}.
% Our results suggest that the cumulative massive BH mass density growing in galactic nuclei also follows
% an exponential evolution with redshift,
% which is statistically in agreement with the host halo and galaxy growth.
The star-to-halo mass ratio is assumed to be $f_\star =0.01$ for those quasar progenitor halos at $z>6$
% (UNIVERSEMACHINE; Behroozi et al. 2019).
\citep[fits by code {\tt UNIVERSEMACHINE} in][]{2019MNRAS.488.3143B}.
%https://ui.adsabs.harvard.edu/abs/2019MNRAS.488.3143B/abstract
With those values, we estimate the stellar-to-BH mass ratio for high-$z$ quasars as
%
\begin{equation}
\frac{\rho_{\star}(z)}{\rho_{\bullet}(z)}
\simeq 2.5\times 10^{3} \left(\frac{f_\star}{0.01}\right)
~ 10^{(k_{\rm h}-k_{\rm M})(z-6)},
\end{equation}
% 
\red{KI: please check the value of $k_{\rm h}-k_{\rm M}$.}
\blue{
where $k_{\rm h} \approx -0.16 $ for the parent halo growth histories.
}
Therefore, at $z\sim 6$ the bulge-to-BH mass ratio $\sim O(10^3)$ for the entire BH population (i.e., low-mass BHs and low-luminosity quasars) 
is broadly consistent with those seen in the local universe, although SMBHs observed as high-$z$ quasars
appear to be overmassive compared to the local relation \citep[e.g.,][]{2013ApJ...773...44W,2020A&A...637A..84P}.

\subsection{Quasar luminosity function}

Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
%The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
\red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
Also, you could compare your results with Aaron Yung's results.}
In the right panel of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
The rapid decline toward higher redshifts is nicely characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{QLF_rhoz.png}
\caption{
{\it Left panel}: quasar luminosity functions at different redshifts of $6\leq z \leq 10$. 
The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
evaluated by the integration of the QLF shown in the left panel.
The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.95$.
This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
}
\label{fig:QLF_rhoz}
\end{figure*}

@@

\clearpage
